Generalized Tractability

### 2023-04-11 GeneralizedTractability_230310.tex
Updates from Overleaf

Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
\[
\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots,
\]
This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.

@@

\section{Main Results}

\subsection{Notation and fundamental definitions}
Let $T$ be a tractability function defined as follows,
\[
T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty),
\]
\fred{I think that we do not need to bound $T$ away from $0$, but doing so may help satisfy \eqref{eq:ptauassume}.}
A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.  Some examples of tractability functions commonly considered are provided in Section \ref{sec:examples}.

@@

Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information-based complexity is not expected to vanish under arbitrarily loose error requirements.  For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation}
	T \text{ is non-decreasing in all variables}
\end{equation}
which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.  Since there are an infinite number of positive eigenvalues, it also make sense to assume that
\begin{equation}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit:
\begin{equation}
	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp).
\end{equation}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}
\end{subequations}

@@

\begin{theorem}\label{thm_main_strong_tract2}
A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
\[
	\cp_{\textup{sopt}} =
	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

\begin{theorem}\label{thm_main_tract2}
A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L_{\vp} > 0$ such that
\begin{equation} \label{eq:tractiff4}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:tractiff4} holds for some $\vp$, let  
\[
\widetilde{\cp}_{\textup{opt}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \text{ and }  \eqref{eq:tractiff4} \text{ does not hold } \forall \vp \in [\vzero,\vp^*/2)\}.
\]
Then $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.
\
\end{theorem}

@@

\begin{theorem}\label{thm:qpt}
A problem is $T$-quasi-polynomial tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ such that
\begin{equation}\label{thmqpt}
M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}
<\infty
\end{equation}
%where $\Bar{p} = -p(1+\log(T(0,d,\vp))$.
If it holds then 
\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
\end{theorem}
\begin{proof}
\textbf{Necessity Condition:}\\
Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
\[
\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}
\quad\quad \forall\varepsilon >0, d\in \mathbb{N}
\] 
Since $\lambda_{i,d}$ are non-increasing, we have
\[
\lambda_{\left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1,d}\leq \varepsilon^2
\]
Given that the estimate holds for all $\varepsilon> 0$, we assume that $\varepsilon \in (0, 1]$.\\

If we vary $\varepsilon\in (0,1]$, we have that
\[
j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1
\] which attains the values $j = j_d,j_{d+1},\dots$, where
\[
j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{ T(0,d,\vp)\}\rfloor + 1
\]
Furthermore, we have
\[j \leq C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{T(\lambda^{-1}_{j,d},d,\vp)\}+1 \]
This implies that
\[
\left(\log\frac{j-1}{C_{\vp}}\right)^\tau \leq \left(T(\varepsilon^{-1},d,\vp)\right)^\tau \leq K_{\vp,\tau}T(\lambda_{j,d},d,\tau\vp) 
\]
we have 
%\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]
\end{proof}

@@

\begin{theorem}\label{thm:subhT}
	The problem is sub-$h \circ T$ tractable if and only if
	\[
	S_c = S_{c,\vp} :=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d},d,\vp))} <\infty \qquad \forall c > 0.
	\]
\end{theorem}
\begin{proof}
We suppress the $\vp$ dependence, because it does not enter into the proof.

@@

Consequently,
\begin{align*}
\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
\\
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \\
& = 0, \qquad \text{since } \lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty.
\end{align*}	
\fred{Maybe this last assumption on $T$ tending to infinity also depends on the additivity or something similar.}  Since $c$ is arbitrary, we have satisfied the condition of Definition \ref{def:subhT}.

@@

For a fixed $d$, the largest the largest $\varepsilon$ can be and still satisfy $ \varepsilon^{-1} + d \ge V_c$ is $\max(V_c - d,1)$.   Let 
\begin{equation} \label{eq:nstardef}
	n^*(d,c) : = n(\max(V_c - d,1),d,c) \le h(cT(\max(V_c-d,1),d)
\end{equation} 
By varying $\varepsilon^{-1}$ in the interval $[\max\{1,V_c-d\},\infty)$,  the integer $	n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.  Thus, 
\begin{align}
		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
		\nonumber
		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
		\intertext{Combining this inequality with ...}
		\nonumber
		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} \\
		\nonumber
		&  = \sup_{d\in\naturals} \left [
		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2c\, T(\lambda_{i,d},d))}
		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} 
		\right]\\
		 \nonumber
		 & \le \sup_{d\in\naturals} \left [
\frac{n^*(d,c)-1}{h(2c\, T(\lambda_{\max},d))}
+ \sum_{i=1}^\infty \frac1{n^2}
\right] 
 \qquad \text{by \eqref{eq:subhTneq}}\\ 
		 & \le \sup_{d\in\naturals} \left [
		 \frac{ h(cT(\max(V_c-d,1),d)}{h(2c\, T(\lambda_{\max},d))}
		\right] + \frac{\pi^2}{6}
		\qquad \text{by \eqref{eq:nstardef}.}
\end{align}
\fred{Here maybe we need additivity of $T$ .  I will pause.}	Moreover,
	\begin{eqnarray*}
		\exp(-2c\, T(0,d^t,\vp))\, (n^*-1) &\le & \exp(-2c\, T(0,d^t,\vp))\, 
		\exp (c\, T(V^s,1,\vp) + c\, T(0,d^t,\vp))\\
		&\le & \exp (c\, T(V^s,1,\vp))\\
		&<& \infty,
	\end{eqnarray*}
	independently of $d$. This implies that 
	\[
	\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))<\infty,
	\]
	also independently of $d$. As $c>0$ was chosen arbitrarily, we can replace $2c$ by $c$ and see
	necessity of the condition in the theorem.

>>>>

Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
\[
\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
\]
This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.

@@

\section{(Strong) Tractability}

\subsection{Notation and fundamental definitions}
Let $T$ be a tractability function defined as follows,
\begin{equation} \label{eq:Tspec}
    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty),
\end{equation}
\fred{I think that we do not need to bound $T$ away from $0$, but doing so may help satisfy \eqref{eq:ptauassume}.}
A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.  Some examples of tractability functions commonly considered are provided in Section \ref{sec:examples}.

@@

Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information-based complexity is not expected to vanish under arbitrarily loose error requirements.  For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation}
	T \text{ is non-decreasing in all variables}
\end{equation}
which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.  Since there are an infinite number of positive eigenvalues, it also make sense to assume that
\begin{equation}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit:
\begin{equation}
	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp).
\end{equation}
\end{subequations}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}

@@

\begin{theorem}\label{thm_main_strong_tract2}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
\[
	\cp_{\textup{sopt}} =
	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

\begin{theorem}\label{thm_main_tract2}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L_{\vp} > 0$ such that
\begin{equation} \label{eq:tractiff4}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:tractiff4} holds for some $\vp$, let  
\[
\widetilde{\cp}_{\textup{opt}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \text{ and }  \eqref{eq:tractiff4} \text{ does not hold } \forall \vp \in [\vzero,\vp^*/2)\}.
\]
Then $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.
\
\end{theorem}

@@

\begin{theorem}\label{thm:qpt}
A problem is $T$-quasi-polynomial tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ such that
\begin{equation}\label{thmqpt}
M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}
<\infty
\end{equation}
%where $\Bar{p} = -p(1+\log(T(0,d,\vp))$.
%If it holds then 
%\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
\end{theorem}
\begin{proof}
\textbf{Necessity Condition:}\\
Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
\[
\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}
\quad\quad \forall\varepsilon >0, d\in \mathbb{N}
\] 
Since $\lambda_{i,d}$ are non-increasing, we have
\[
\lambda_{\left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1,d}\leq \varepsilon^2
\]
Given that the estimate holds for all $\varepsilon> 0$, we assume that $\varepsilon \in (0, 1]$.\\

If we vary $\varepsilon\in (0,1]$, we have that
\[
j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1
\] which attains the values $j = j_d,j_{d+1},\dots$, where
\[
j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{ T(0,d,\vp)\}\rfloor + 1
\]
Furthermore, we have
\[j \leq C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{T(\lambda^{-1}_{j,d},d,\vp)\}+1 \]
This implies that for $\tau>1$, we have
%\[\left(\log\frac{j-1}{C_{\vp}}\right)^\tau \leq \left(T(\varepsilon^{-1},d,\vp)\right)^\tau \leq K_{\vp,\tau}T(\lambda_{j,d},d,\tau\vp) \]
we have 
%\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]
\end{proof}

@@

\begin{theorem}\label{thm:subhT}
	Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions}.  Moreover, let $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ for all $\varepsilon > 0$.  The problem is sub-$h \circ T$ tractable if and only if
	\[
	S_c = S_{c,\vp} :=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d},d,\vp))} <\infty \qquad \forall c > 0.
	\]
\end{theorem}
\begin{proof}
We suppress the $\vp$ dependence, because it does not enter into the proof.

@@

Consequently,
\begin{align}
\nonumber
\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
\\
\nonumber
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \label{eq:alastone}.
\end{align}	
The finiteness of $S_c$ implies that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$.  Together with the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$, we can infer that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.  This implies that the limit in \eqref{eq:alastone} vanishes.  Since $c$ is arbitrary, we have satisfied the condition of Definition \ref{def:subhT}.

@@

For a fixed $d$, define $\varepsilon^{-1}_{\max,d} = \max(V_c - d,\lambda_{\max}^{-1})$.  the largest the largest $\varepsilon$ can be and still satisfy $ \varepsilon^{-1} + d \ge V_c$ is $\max(V_c - d,1)$.   Let 
\begin{equation} \label{eq:nstardef}
	\varepsilon^{-1}_{\max,d} := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max,d},d,c) \le h(cT(\varepsilon^{-1}_{\max,d},d)).
\end{equation} 
By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max,d},\infty)$,  the integer $n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.  Thus, 
\begin{align}
		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
		\nonumber
		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
		\intertext{Combining this inequality with the upper bound on $n^*(d,c)$ yields}
		\nonumber
		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} \\
		\nonumber
		&  = \sup_{d\in\naturals} \left [
		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} 
		\right]\\
		 \nonumber
		 & \le \sup_{d\in\naturals} \left [
\frac{n^*(d,c)-1}{h(2cT(\lambda_{\max}^{-1},d))}
+ \sum_{i=1}^\infty \frac1{n^2}
\right] 
 \qquad \text{by \eqref{eq:subhTneq}}\\ 
 \label{eq:lastone}
		 & \le \sup_{d\in\naturals} \left [
		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
		\right] + \frac{\pi^2}{6}
		\qquad \text{by \eqref{eq:nstardef}.}
\end{align}

Note that 
\[
\varepsilon^{-1}_{\max,d} = \max(V_c - d,\lambda_{\max}^{-1}) 
= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^* : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\} \\
\lambda_{\max}^{-1}, & d \in \{d^*+1, \ldots\}
\end{cases}
\]
Recalling that $T$ is non-decreasing in it's arguments, this implies that 
\begin{align*}
    \sup_{d\in\naturals} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
  &\le \max \left \{  
  \sup_{d \in \{1, \ldots, d^*\}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}, 
  \sup_{d\in \{d^*+1, \ldots \}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
  \right \} \\
  & \le \max \left \{  
  \sup_{d \in \{1, \ldots, d^*\}}  \,
		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{\max}^{-1},d))}
  , 
  \sup_{d\in \{d^*+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{h(2cT(\lambda_{\max}^{-1},d))}
  \right \}
  \\
  & \le \max \left \{  
		 \frac{ h(cT(V_c,d^*))}{h(2cT(\lambda_{\max}^{-1},1))}, 
  \sup_{d\in \{d^*+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{[h(cT(\lambda_{\max}^{-1},d))]^2}
  \right \} \\
  & = \max \left \{  
		 \frac{ h(cT(V_c,d^*))}{h(2cT(\lambda_{\max}^{-1},1))}, 
  \sup_{d\in \{d^*+1, \ldots \}} \,
		 \frac{1}{h(cT(\lambda_{\max}^{-1},d))}
  \right \} \\
  & < \infty \qquad \text{since }h \ge 1.
\end{align*}
Combining this bound with \eqref{eq:lastone} establishes the finiteness of $S_2c$ and completes the proof of the necessary condition.
